---
title: "Assignment 1"
author: "James Bond (st.number 007)"
date: "1 January 2033"
output: pdf_document
fontsize: 11pt
highlight: tango
---

```{r}
data_path = "./data/"
birth_data = read.table(paste(data_path, "birthweight.txt", sep=""), header = TRUE)
austen_data = read.table(paste(data_path, "austen.txt", sep=""), header = TRUE)
weather_data = read.table(paste(data_path, "weather.txt", sep=""), header = TRUE)

```

### Exercise 1.1

(a) 

-   The data seems to be normally distributed as a qqplot shows a roughly straight line (see figure below)
-   using the mean() function yields a points estimate of **2913.293** for the mean weight (in grams).

```{r}
# summary(birth_data)
# check the normality of the data through a qqplot.
qqplot = qqnorm(birth_data$birthweight)
mean_point_estimate = mean(birth_data$birthweight)
```

(b) We get a confidence interval of 2913.293 plm 1147.286 at a confidence level of 90%.

```{r}
standard_error_estimate = sd(birth_data$birthweight) / sqrt(length(birth_data))
ninty_five_quantille = qnorm(0.95, mean_point_estimate, standard_error_estimate) # 95, because we want to keep 10% in total when whe sum the left-overs on both sides of the distribution.
upper_range = ninty_five_quantille - mean_point_estimate
upper_range

```

(c) Assuming a theoretical mean of 2800 (the null hypothesis) and an alternative hypothesis stating that m \> 2800, a one sample, one-tailed t-test yields a p-value of \< 2.2e-16. This means that under the null-hypothesis, it is very unlikely that we would observe the sample data. Assuming a standard confidence interval of 95%, we would reject the null-hypothesis based on this t-test and agree with the expert that the mean birth weight is likely higher than 2800 grams.

```{r}
# H0: m = 2800
# Ha: m > 2800
# This thus implies a one-tailed t-test.
t.test(birth_data$birthweight, alternative="greater", mu: 2800)
```

# Note that for 1.2, since we are dealing with a proportionality parameter, we cannot simply use the standard deviation of the samples to estimate the standard error.

```{r}
```


```{r}
